\documentclass[12pt]{article} %Sets the default text size to 11pt and class to article.
%------------------------Dimensions--------------------------------------------
\topmargin=0.0in %length of margin at the top of the page (1 inch added by default)
\oddsidemargin=0.0in %length of margin on sides for odd pages
\evensidemargin=0in %length of margin on sides for even pages
\textwidth=6.2in %How wide you want your text to be
\marginparwidth=0.5in
\headheight=0pt %1in margins at top and bottom (1 inch is added to this value by default)
\headsep=0pt %Increase to increase white space in between headers and the top of the page
\textheight=9.7in %How tall the text body is allowed to be on each page
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\setitemize{noitemsep,topsep=6pt,parsep=0pt,partopsep=0pt}

\begin{document}
%These two pieces of code tell LaTeX that everything that goes in between these tags is what you want displayed as your actual document.
%\thispagestyle{empty} %removes the page number

\centerline{{\Huge \sc Jordan Heinrichs}}  %Makes whatever text you put in parenthesis move to the center
%Prevents the following text from being indented
%This is the same as a return in Latex
\centerline{Phone: (403) 399-6280} %1234 Generic St. \textbullet \hspace{5pt}Boulder, CO 80303 \textbullet \hspace{5pt}
\centerline{mail@jordanheinrichs.com}
\noindent
\line(1,0){470}\\

\medskip
\noindent {\Large \bf Objective} %Don’t indent this line and make it bold and large
\medskip %This creates a small gap but not quite as large as a return (it’s a space saver)

\noindent To obtain an internship in electrical or computer engineering field where I can demonstrate my hard work and ability to quickly learn whatever task is given to me. Throughout the internship, to gather experience in the engineering field to contribute my best toward the success of the organization.  

  \bigskip
\noindent{\Large \bf Education}
\medskip

\noindent \centerline{ \bf University of Calgary \hfill 2011-Present}
\begin{itemize}[noitemsep,parsep=0pt,partopsep=0pt] %[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
  \item Bachelor of Science, Electrical Engineering with a Computer Engineering Minor
  \item Expected graduation, April 2016 (including internship)
  \item GPA: 3.9/4.0 Cumulative
\end{itemize}


\bigskip %This makes a large line-skip (\smallskip is also a command but has a smaller gap
\noindent{\Large\bf Internship Status}
\medskip

\noindent
\begin{itemize}[noitemsep]
\item Third year complete as of April 30, 2014
\item Seeking internship for 16 months
\item Available May 1, 2014
\end{itemize}

\bigskip
\noindent{\Large \bf Skills} 
\medskip
\begin{itemize}[noitemsep]
\item Very competent programming using C++, C, and Matlab. 
\item Experienced with embedded systems.
\item Strong problem solving and troubleshooting skills.
\item Passion for electrical and software fields.
\bigskip
\item Reliably and dependable. 
\item Very hardworking and motivated.
\item Can learn and adapt quickly to challenges.
\item Personable, works well in group or alone.
\end{itemize}
\noindent %Make sure that there is no line-skip for as long as you want this effect


\bigskip
\noindent{\Large \bf Work Experience} 
\medskip

\noindent \centerline{ \bf NSERC Research,University of Calgary \hfill May - Aug 2013}
\indent \emph{ Summer Student } 
\begin{itemize}[noitemsep]
  \item Developed and executed tests to determine accuracy of a hexacopter dropping sensor nodes.
  \item Troubleshooted and solved problems with hexacopter.
  \item Created a program to capture position of hexacopter using video tracking with C++ OpenCV.
  \item Analysis of data using Matlab and C++.
  \item Presented results and data in meetings and reports.
\end{itemize}

\noindent \centerline{ \bf Whole Foods Market, Penticton BC \hfill Sept 2008 - Aug 2011, May - Aug 2012}
\indent \emph{Stocker, Cashier}
\begin{itemize}[noitemsep]
  \item Responsible for making sure all extra stock put on the shelf when possible.
  \item Received orders and created sales displays.
  \item Flexible, filled many roles. Cashier when needed.
  \item Developed communication skills for maintaining customer satisfaction.
  \item Trained new employees, worked well in a group or on my own.
\end{itemize}

\noindent \centerline{ \bf Penticton Herald, Penction BC \hfill May 2006 - Aug 2007}
\indent \emph{ Paper Deliverer}
\begin{itemize}[noitemsep]
  \item Delivered papers seven days a week before 7:15 am.
  \item Demonstrated reliability.
  \item Worked independently to get the route done.
\end{itemize}

%\smallskip %This makes a large line-skip (\smallskip is also a command but has a smaller gap
\bigskip
\noindent{\Large \bf Extracurricular Activities}
\bigskip

\noindent \centerline{\bf University of Calgary Solar Car Electrical Team \hfill Sept 2013 - Present}
\begin{itemize}[noitemsep]
  \item Developing a GUI interface to read data transmitted over WiFi.
  \item Using C++ QT framework. 
  \item Designing the program from scratch.
\end{itemize}

\noindent \centerline{\bf Many Mini Bots \hfill Sept 2013 - Present}
\begin{itemize}[noitemsep]
  \item A group dedicated for producing and interfacing many small bots.
  \item Building a tricopter for the group.
  \item Carefully documenting my work so they can reproduce it.
\end{itemize}

\noindent \centerline{ \bf Micro Processing Group \hfill Sept 2012 - Present}
\begin{itemize}[noitemsep]
  \item Assembled a surface mount board, learned to solder 0603 parts.
  \item Learning how to use an ARM Cortex M3 processor.
  \item Gaining experience using ANT radio and LCD peripherals.
\end{itemize}


\noindent \centerline{ \bf Schulich Aerodesign Team \hfill Sept 2011 - Aug 2013}
\begin{itemize}[noitemsep]
  \item Received hands on experience  designing and assembling a radio controlled aircraft.
  \item Built two, greater than 2 meter wingspan RC plans for SAE Aerodesign Heavy Life Competition.
  \item Dealt with very limited resources and design constraints throughout the project.
  \item Was a key member of the build team.
\end{itemize}

\bigskip
\noindent{\Large \bf Hobbies}
\medskip
\begin{itemize}
\item Back-country hiking and camping.
\item Long distance running.
\item Building computers.
\end{itemize}
\bigskip

\noindent{\Large \bf Honours/Awards}
\medskip
\noindent
\begin{itemize}[noitemsep]
\item Dean Wirasinghe Undergraduate Scholarships in Engineering 2013
\item CNOOC Undergraduate Scholarships 2013
\end{itemize}

\end{document}	